---
title: "Lab 01 - Hello R"
author: "John T. Bennett"
date: "Feb 4, 2022"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
#library(dplyr)
#install.packages('dplyr')
```

## Exercises

### Exercise 1

```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
#help(datasaurus_dozen)
#View(datasaurus_dozen)
#str(datasaurus_dozen)
```

1a) Based on the help file, how many rows and how many columns does the datasaurus_dozen file have?
1846 rows and 3 columns / variables

1b) What are the variables included in the data frame?
dataset indicating which dataset the data are from, x-values, y-values

### Exercise 2


```{r plot-dino, fig.height=4, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
r= -0.0645

### Exercise 3

```{r plot-star, fig.height=4, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
     geom_point()
```

Correlation coefficient between x and y for this dataset: 
```{r cor-star}
 star_data %>%
     summarize(r = cor(x, y))
```
r= -0.063

### Exercise 4

```{r, fig.height=4, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
     geom_point()
```

Correlation coefficient between x and y for this dataset: 
```{r cor-circle}
 circle_data %>%
     summarize(r = cor(x, y))
```
r= -0.068

### Exercise 5

```{r, fig.height=4, fig.width=6}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Summary correlation coefficients:
```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

For the figure size portion: I've gone with a figure size of 4X6, at least for this lab. 
